```{r solution, echo = FALSE, results = "hide"}
library(tidyquant)

# print available indices
available_index <- tq_index_options()

my_index <- sample(available_index, 1)

# get components of "DOWJONES"
comp_idx <- tq_index(my_index)

highest_weight <- comp_idx$company[which.max(comp_idx$weight)]

my_sol <- highest_weight 
```

```{r datageneration, echo = FALSE, results = "hide"}
my_answers <- afedR::make_random_answers(my_sol, 
                                  candidates = comp_idx$company)
```

Question
========

Using function `tidyquant::tq_index`, download current composition of index `r my_index`. What is the company with the highest percentage in the composition of the index? 

Be aware that the answer is time-dependent and the reported result might be different from what you actually got in your R session.

```{r questionlist, echo = FALSE, results = "asis"}
exams::answerlist(my_answers, markup = "markdown")
```

Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: schoice
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "tidyquant"
exshuffle: TRUE

