```{r solution, echo = FALSE, results = "hide"}
library(BatchGetSymbols)

first_date <- '2019-01-01'
last_date  <- '2020-01-01'

my_tickers <- c('AAPL', 'BAC', 
                'GE', 'TSLA',
                'SNAP')
	
df_prices <- BatchGetSymbols(tickers = my_tickers, 
                             first.date = first_date, 
                             last.date = last_date)[[2]]

split_l <- split(df_prices, df_prices$ticker)

my_fct <- function(df_in) {
  price_vec <- df_in$price.adjusted
  ticker_in <- df_in$ticker[1]
  
  total_ret <- last(price_vec)/first(price_vec) - 1
  
  return(tibble(ticker = ticker_in,
                total_ret = total_ret))
}

df_results <- bind_rows(
  lapply(split_l, my_fct)
)

winner <- df_results$ticker[which.max(df_results$total_ret)]

my_sol <- winner
```

```{r datageneration, echo = FALSE, results = "hide"}
my_answers <- afedR::make_random_answers(my_sol, candidates = unique(df_results$ticker))
```

Question
========

Using again the `BatchGetSymbols` package, download data between `r first_date` and `r last_date` for the following tickers:

- AAPL: Apple Inc
- BAC:	Bank of America Corporation
- GE:	General Electric Company
- TSLA:	Tesla, Inc.
- SNAP:	Snap Inc.

Using the **adjusted closing price** column, what company provided higher return to the stock holder during the analyzed period? 

Tip: this is an advanced exercise that will require some coding. To solve it, check out function `split` to split the dataframe of price data and `lapply` to map a function to each dataframe.


```{r questionlist, echo = FALSE, results = "asis"}
exams::answerlist(my_answers, markup = "markdown")
```

Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: schoice
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "batchgetsymbols 2"
exshuffle: TRUE

