```{r datageneration, echo = FALSE, results = "hide"}
# no datageneration

```

Question
========

Create a `dataframe` with the following code:

```{r, eval=FALSE}
library(dplyr)

my_N <- 10000
my_df <- tibble(x = 1:my_N,
                y = runif(my_N))
```

Export the resulting `dataframe` to each of the five formats: csv, rds, xlsx, fst. Which of the formats took up the most space in the computer's memory? Tip: `file.size` calculates the size of files within R.


Solution
================

```{r, eval=FALSE}
library(tidyverse)

do_tests <- function(my_N) {
  
  my_df <- tibble(x = 1:my_N,
                  y = runif(my_N))
  
  # csv
  my_f <- tempfile(pattern = 'temp', fileext = '.csv')
  time.csv <- system.time({
    write_csv(my_df, my_f)
  })['elapsed']
  size.csv <- file.size(my_f)/1000000
  
  # rds
  my_f <- tempfile(pattern = 'temp', fileext = '.rds')
  time.rds <- system.time({
    write_rds(my_df, my_f)
  })['elapsed']
  
  size.rds <- file.size(my_f)/1000000
  
  # xlsx
  my_f <- tempfile(pattern = 'temp', fileext = '.xlsx')
  library(writexl) 
  time.xlsx <- system.time({
    write_xlsx(my_df, my_f)
  })['elapsed']
  
  size.xlsx <- file.size(my_f)/1000000
  
  # fst
  library(fst)
  my_f <- tempfile(pattern = 'temp', fileext = '.fst')
  time.fst <- system.time({
    write_fst(my_df, my_f)
  })['elapsed']
  
  size.fst <- file.size(my_f)/1000000
  
  print(c(size.csv, size.rds, size.xlsx, size.fst))
  
  print(c(time.csv, time.rds, time.xlsx, time.fst))
  
  tab <- tibble(Result = c('csv', 'rds', 'xlsx', 'fst'), 
                Size =  c(size.csv, size.rds, size.xlsx, size.fst),
                Time = c(time.csv, time.rds, time.xlsx, time.fst))
  
  return(tab)
}

my_N <- 10000

tab <- do_tests(my_N)
print(tab)

my_msg <- paste0('The format with largest disk space for N = ', my_N, ' is ', 
                 tab$Result[which.max(tab$Size)], '.')
message(my_msg)

```


Meta-information
================
extype: string
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "export file"
exshuffle: TRUE

