```{r solution, echo = FALSE, results = "hide", message=FALSE}
library(tidyverse)

my_l <- list(df1 = tibble(x = 1:100, 
                          y = runif(100)),
             df2 = tibble(x = 1:100, 
                          y = runif(100), 
                          v = runif(100)),
             df3 = tibble(x = 1:100, 
                          y = runif(100), 
                          z = runif(100)) )

# solution with bind_rows
bind_df1 <- bind_rows(my_l)

# solution with do.cal
bind_df2 <- do.call(bind_rows, my_l)

# check solutions match
identical(bind_df1, bind_df2)

print(bind_df1)
# the missing data points were set as NA values
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
my_answers <- rep(0, 5)
```

Question
========

Consider the following list:

```{r}
library(tidyverse)

my_l <- list(df1 = tibble(x = 1:100, y = runif(100)),
             df2 = tibble(x = 1:100, y = runif(100), v = runif(100)),
             df3 = tibble(x = 1:100, y = runif(100), z = runif(100)) )
```

Add all `dataframes` in `my_l` to a single object using `do.call` or `dplyr::bind_rows` functions. What happened to the `df1` data where `v` and `z` columns do not exist?


Solution
================

When `bind_rows` does not find the same column at the junction of different tables, the missing data is defined as `NAs`. See below:

```{r solution, eval=FALSE}
```


Meta-information
================
extype: string
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "function 01"
exshuffle: TRUE

