```{r solution, echo = FALSE, results = "hide", message=FALSE}
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
my_answers <- rep(0, 5)
```

Question
========

Consider the `dataframe` created with the following code:

```{r, eval=FALSE}
library(tidyverse)

my_N <- 100

df <- bind_rows(tibble(ticker = rep('STOCK 1', my_N),
                       ref_date = Sys.Date() + 1:my_N,
                       price = 100 + cumsum(rnorm(my_N))),
                tibble(ticker = rep('STOCK 2', my_N),
                       ref_date = Sys.Date() + 1:my_N,
                       price = 100 + cumsum(rnorm(my_N))) )

print(df)
```

Is the `dataframe` format long or wide? Explain your answer.


Solution
================

The format is long: we have data stacked for two different stocks. Note that, with the addition of new tickers, the table grows with new lines. New variables can be easily added with new columns.


```{r solution, eval=FALSE}
```


Meta-information
================
extype: string
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "function 01"
exshuffle: TRUE

