```{r solution, echo = FALSE, results = "hide", message=FALSE, eval=FALSE}
library(BatchGetSymbols)
library(tidyverse)

df_sp500 <- GetSP500Stocks()

my_tickers <- df_sp500$Tickers

future::plan(future::multisession, 
             workers = floor(parallel::detectCores()/2))

first_date <- '2015-01-01'
df_prices <- BatchGetSymbols(tickers = my_tickers, 
                             first.date = first_date, 
                             last.date = Sys.Date(),
                             freq.data = 'yearly', 
                             do.parallel = TRUE)[[2]]

tab <- df_prices %>%
  na.omit() %>%
  group_by(ticker) %>%
  summarise(mean = mean(ret.adjusted.prices),
            sd = sd(ret.adjusted.prices))

p <- ggplot(tab, aes(x = sd, y = mean)) + 
  geom_point() + 
  xlim(0, 0.5) + ylim(-0.5, 0.5)

print(p)
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
my_answers <- rep(0, 5)
```

Question
========

Use the `BatchGetSymbols::GetSP500Stocks` function to discover all tickers currently belonging to the SP500 index. Using `BatchGetSymbols`, download the annual return data for all stocks in the index, from `r '2015-01-01'` to the current day. After that, create the average/variance map by plotting the average annual return as the y axis and the standard deviation as the x axis. Tip: Use the parallel option in `BatchGetSymbols` to speed up the execution of the code. Also, you will find many outliers in the raw data. Make sure that the graph is visible limiting the x and y axes (see the `ggplot2::xlim` and `ggplot2::ylim` functions).


Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: string
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "function 01"
exshuffle: TRUE

