```{r datageneration, echo = FALSE, results = "hide"}
my_answers <- c('S+', 
                'C++',
                'Python',
                'Matlab',
                'Javascript')

#check_answers(my_answers)
```

Question
========

Based on the study proposed earlier, create a directory structure on your computer to accommodate the study. Create mock files for each subdirectory (see directory structure at section \@ref(directories)). Be aware you can create mock files and direction all in R (see functions `cat` and `dir.create`).

```{r questionlist, echo = FALSE, results = "asis"}
exams::answerlist(my_answers, markup = "markdown")
```

Solution
================

```{r, eval=FALSE}
library(fs)

# set temp dir for solving exercise
temp_dir <- path(tempdir(), 'Chapter 3 exercise')

# create folder
dir_create(temp_dir)

# create files
file_create(path(temp_dir, '01-import_data.R'))
file_create(path(temp_dir, '02-clean_data.R'))
file_create(path(temp_dir, '03-build_budget_table.R'))
file_create(path(temp_dir, '04-build_investment_realstate_table.R'))
file_create(path(temp_dir, '05-build_report.R'))

# create dirs
dir_create(path(temp_dir, 'data'))
dir_create(path(temp_dir, 'tabs'))
dir_create(path(temp_dir, 'figs'))

# fill with files
for (i_year in 2009:2019) {
  file_create(path(temp_dir, 'data', 
                   paste0('annual_budget_', i_year, '.xlsx')) )
}

file_create(path(temp_dir, 'data', 'fixed_income_index.csv'))
file_create(path(temp_dir, 'data', 'real_state_data.rds'))
file_create(path(temp_dir, 'figs', 'Income_and_HousePrices.png'))
file_create(path(temp_dir, 'tabs',  'Table_with_Results.xlsx'))

dir_tree(temp_dir)
```

Meta-information
================
extype: string
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "folders"
exshuffle: TRUE

