```{r solution, echo = FALSE, results = "hide", message=FALSE, eval=FALSE}
library(BatchGetSymbols)
library(tidyverse)

tickers <- sample(GetSP500Stocks()$Tickers, 4)
first_date <- Sys.Date() - 3*365
last_date  <- Sys.Date()

df_stocks <- BatchGetSymbols(tickers = tickers, 
                             first.date = first_date, 
                             last.date = last_date)[[2]]

my_tab <- df_stocks %>%
  na.omit() %>%
  group_by(ticker) %>%
  do(my_arima = arima(x = .$ret.adjusted.prices, 
                      order = c(1, 0, 1))) 

glimpse(my_tab)

# solution
library(texreg)

screenreg(my_tab$my_arima)
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
#my_answers <- make_random_answers(my_sol)
my_answers <- rep(NA, 5)

type_question <- 'string'
ex_name <- 'reporting 12-02'
```

Question
========

Using the `BatchGetSymbols::GetSP500Stocks` function, select 4 stocks at random and download the adjusted price data for the last three years. Estimate an ARIMA(1, 0, 1) model for each stock and report the result on the R screen with the `texreg::screenreg` function.


Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: `r type_question`
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: `r ex_name`
exshuffle: TRUE

