```{r solution, echo = FALSE, results = "hide", message=FALSE, eval=FALSE}
library(Quandl)
library(memoise)
library(tictoc)

mem_quandl <- memoise(f = Quandl, cache = cache_memory())

id <- 'FRED/DDOE01USA086NWDB'

tic('Using original Quandl')
df <- Quandl(code = id)
toc()

tic('Using memoise version (first call)')
df <- mem_quandl(code = id)
toc()

tic('Using memoise version (second call)')
df <- mem_quandl(code = id)
toc()
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
#my_answers <- make_random_answers(my_sol)
my_answers <- rep(NA, 5)

type_question <- 'string'
ex_name <-  'otimizing 13-04'
```

Question
========

Use the `memoise` package to create a memorized version of function `Quandl::Quandl`. Use the new function to import data about the United States Consumer Price Index (quandl code `'FRED/DDOE01USA086NWDB'`). How much percentage speed gain do you get from the second call to the memorized version?


Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: `r type_question`
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: `r ex_name`
exshuffle: TRUE

