```{r solution, echo = FALSE, results = "hide", message=FALSE, eval=FALSE}
library(Rcpp)

cppFunction('Rcpp::NumericVector sum_vectors_C(NumericVector x, NumericVector y) {
  int n = x.size();
  
  Rcpp::NumericVector total(x.size());
  
  for(int i = 0; i < n; ++i) {
    total[i] = x[i] + y[i];
  }
  return total;
}')

x <- runif(100)
y <- runif(100)

sol_C <- sum_vectors_C(x, y)
sol_R <- x + y

identical(sol_C, sol_R)
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
#my_answers <- make_random_answers(my_sol)
my_answers <- rep(NA, 5)

type_question <- 'string'
ex_name <- 'otimizing 13-02'
```

Question
========

Use the `Rcpp` package to write a C++ language function that will add elements of two numerical vectors. The output must be another vector of the same size and with elements equivalent to the `x + y` operation. Use the `identical` function to test that all elements of both vectors are equal.


Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: `r type_question`
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: `r ex_name`
exshuffle: TRUE

