```{r solution, echo = FALSE, results = "hide", message=FALSE, eval=FALSE}
library(Rcpp)

cppFunction('Rcpp::NumericVector sum_vectors_C(NumericVector x, NumericVector y) {
  int n = x.size();
  
  Rcpp::NumericVector total(x.size());
  
  for(int i = 0; i < n; ++i) {
    total[i] = x[i] + y[i];
  }
  return total;
}')

x <- runif(100)
y <- runif(100)

sol_C <- sum_vectors_C(x, y)
sol_R <- x + y

identical(sol_C, sol_R)

library(tictoc)

tic('Using Rcpp')
sol_C <- sum_vectors_C(x, y)
toc()

tic('Using base R')
sol_R <- x + y
toc()

tic('Using a loop and prealocation')
sol_loop <- numeric(length = length(x))
for (i in 1:length(x)) {
  sol_loop[i] <- x[i] + y[i]
}
toc()
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
#my_answers <- make_random_answers(my_sol)
my_answers <- rep(NA, 5)

type_question <- 'string'
ex_name <- 'otimizing 13-03'
```

Question
========

Use the `tictoc` package to compare the performance of the previous function with the native operator `+`, and a loop-based version with the pre-allocation of the result vector. Which alternative has the shortest execution time and why? Does the `Rcpp` version beat the loop version?


Solution
================

The best way to add vectors is with the native operator `+`, which is already optimized for fast executions.


```{r solution, eval=FALSE}
```


Meta-information
================
extype: `r type_question`
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: `r ex_name`
exshuffle: TRUE

