```{r datageneration, echo = FALSE, results = "hide"}
my_answers <- c('Compile R packages locally', 
                'Compile graphics.',
                'Make coffee (?).',
                'Build web pages.',
                'Compile technical reports.')

#check_answers(my_answers)
```

Question
========

On the [CRAN site](https://cloud.r-project.org/bin/windows/) you can also install the Rtools application. What is it for?


```{r questionlist, echo = FALSE, results = "asis"}
exams::answerlist(my_answers, markup = "markdown")
```

Solution
================

Rtools is an extension particular to R on Windows. It is used to compile packages from source code and is a requirement for those who develop packages. For the average user, however, it is also recommended to install Rtools as some packages require such compilation.

For Linux/Unix or MacOS users, Rtools is not necessary as, generally, compilers are already available by the operating system itself.


Meta-information
================
extype: schoice
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "rtools"
exshuffle: TRUE

