```{r datageneration, echo = FALSE, results = "hide"}
my_answers <- c('It was designed for analyzing data and producing statistical output', 
                'Easy to use',
                'Quick code execution',
                'Makes it easy to write mobile apps',
                'Works on any plataform such as Windows, Unix, MacOS')

#check_answers(my_answers)
```

Question
========

Why is R special when comparing to other programming languages, such as Python, C++, javascript and others?


```{r questionlist, echo = FALSE, results = "asis"}
exams::answerlist(my_answers, markup = "markdown")
```

Solution
================

Undoubtedly, the main differential of the R language is the ease with which data can be analyzed on the platform. Although other languages also allow data analysis, it is in R where this process is supported by a wide range of specialized packages.

Meta-information
================
extype: schoice
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "about R"
exshuffle: TRUE

