```{r datageneration, echo = FALSE, results = "hide"}
# no datageneration
```

Question
========

Use the `install.packages` function to install the `BatchGetSymbols` package on your computer. After installation, use function `BatchGetSymbols` to download price data for the IBM stock in the last 15 days. Tips: 1) use function `Sys.Date()` to find out the current date and `Sys.Date()- 15` to calculate the date located 15 days in the past; 2) note that the output of `BatchGetSymbols` is a list -- a special type of object -- and that the price data is located in the second element of that list.



Solution
================


```{r, eval=FALSE}
if (!require(BatchGetSymbols)) install.packages('BatchGetSymbols')

l_out <- BatchGetSymbols(tickers = 'IBM',
                         first.date = Sys.Date() - 15,
                         last.date = Sys.Date())

df_prices <- l_out[[2]]
str(df_prices)
```


Meta-information
================
extype: string
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "install pkgs"
exshuffle: TRUE

