```{r datageneration, echo = FALSE, results = "hide"}
# no datageneration
```

Question
========

Use the `unzip` function to unzip the downloaded file from previous question to a directory called` 'afedR-files'` inside the "Desktop" folder. How many files are available in the resulting folder? Tip: use the `recursive = TRUE` argument with `list.files` to also search for all available subdirectories.


Solution
================

```{r, eval=FALSE}
my_folder <- '~/Desktop/adfeR-Files' # this is probably C:/Users/USERNAME/Desktop for Windows
unzip(local_file, exdir = my_folder) # local_file comes from previous exercise

files <- list.files(my_folder, 
                    full.names = TRUE, 
                    recursive = TRUE)

n_files <- length(files)

message(paste0('There are ', n_files, ' files available at folder "', my_folder, '".'))
```


Meta-information
================
extype: string
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "unzip"
exshuffle: TRUE

