```{r solution, echo = FALSE, results = "hide", message = FALSE}
#if (!require(cranlogs)) install.packages('cranlogs')

pkgs <- cranlogs::cran_top_downloads(when = 'last-month')

my_sol <- pkgs$package[1]

```

```{r datageneration, echo = FALSE, results = "hide"}
my_answers <- make_random_answers(my_sol, unique(pkgs$package))

check_answers(my_answers)
```

Question
========

The `cranlogs` package allows access to downloads statistics of CRAN packages. After installing `cranlogs` on your computer, use the `cranlogs::cran_top_downloads` function to check which are the 10 most installed packages by the global community in the last month. Which package comes first? Tip: Set the `cran_top_downloads` function input to `when = 'last-month'`. Also, be aware that the answer here may not be the same as you got because it depends on the day the R code was executed.

```{r questionlist, echo = FALSE, results = "asis"}
exams::answerlist(my_answers, markup = "markdown")
```

Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: schoice
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "install pkgs 03"
exshuffle: TRUE

