```{r solution, echo = FALSE, results = "hide"}
library(BatchGetSymbols)
library(tidyverse)

first_date <- '2010-01-01'
last_date <- '2020-12-31'

df_prices <- BatchGetSymbols(tickers = 'GOOG', 
                             first.date = first_date,
                             last.date = last_date)[[2]]

value_purchase <- 1000

# solution
my_sol <- last(df_prices$price.adjusted)/first(df_prices$price.adjusted)*value_purchase
```

```{r datageneration, echo = FALSE, results = "hide"}
my_answers <- afedR::format_cash(
  as.numeric(afedR::make_random_answers(my_sol)), 
  type_cash = 'USD')

#check_answers(my_answers)
```


Question
========

Use the `BatchGetSymbols` package to download Google (GOOG) stock data, from` r first_date` to `r last_date`. If the investor had bought 1000 USD in Google shares on the first day of the data and kept the investment until today, what would be the value of his portfolio?

```{r questionlist, echo = FALSE, results = "asis"}
exams::answerlist(my_answers, markup = "markdown")
```

Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: schoice
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "batchgetsymbols"
exshuffle: TRUE

