```{r solution, echo = FALSE, results = "hide", message=FALSE, eval=FALSE}
say_my_name <- function(name_in) {
  # Prints a single name in the prompt
  #
  # ARGS: name_in - Name to be printed
  # RETURNS: TRUE, if sucessfull
  
  # check inputs
  if (class(name_in) != 'character') {
    stop('Class of input name_in is ', class(name_in), 
         ' and not character!')
  }
  
  if (length(name_in) > 1) {
    stop('Input name_in has length ', length(name_in), 
         ' and not 1 (this function only works for one name)!')
  }
  
  
  
  my_msg <- paste0('Your name is ', name_in, '.')
  
  message(my_msg)
  
  # invisible makes sure the fct doesnt return anything if not output is set
  return(invisible(TRUE))
}

library(tidyverse)

# get CURRENT url from https://data.chhs.ca.gov/dataset/most-popular-baby-names-2005-current
my_url <- 'https://data.brasil.io/dataset/genero-nomes/grupos.csv.gz'

df_names <- read_csv(my_url, col_types = cols())

my_names <- sample(df_names$name, 15)

for (i_name in my_names) {
  
  say_my_name(i_name)
}
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
my_answers <- rep(NA, 5)

```

Question
========

In the database of [Brasil.IO](https://data.brasil.io/dataset/genero-nomes/groups.csv.gz)^[https://data.brasil.io/dataset/genero-nomes/groups.csv.gz] you will find a table with names and genres. Import the data from the file and, using a loop, apply  function `say_my_name` to 15 random names in the database. Tip:  you can read the data directly from the link using `readr::read_csv(LINK)`.


Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: string
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "function 04"
exshuffle: TRUE

