```{r solution, echo = FALSE, results = "hide", message=FALSE, eval=FALSE}
library(BatchGetSymbols)

indexes <- c('^BVSP', '^GSPC', '^FTSE', '^N225')

df_indices <- BatchGetSymbols(tickers = indexes, 
                              first.date = '2010-01-01',
                              last.date = Sys.Date())[[2]]

tab <- tibble()
for (index in indexes) {
  
  temp_df <- df_indices %>%
    filter(ticker == index)
  
  avg_ret <- mean(temp_df$ret.adjusted.prices, 
                  na.rm = TRUE)
  max_ret <- max(temp_df$ret.adjusted.prices, 
                 na.rm = TRUE)
  min_ret <- min(temp_df$ret.adjusted.prices, 
                 na.rm = TRUE)
  
  # save result
  tab <- bind_rows(tab, tibble(index = index,
                               mean_ret = avg_ret, 
                               max_ret = max_ret, 
                               min_ret = min_ret))
  
}

print(tab)
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
my_answers <- rep(NA, 5)

```

Question
========

Use the `BatchGetSymbols` package to download data from the SP500 (`'^GSPC'`), Ibovespa (`'^BVSP'`), FTSE (`'^ FSTE'`) and Nikkei 225 (`'^N225'` index)) from '2010-01-01'` to the current date. With the imported data, use a loop to calculate the average, maximum and minimum return for each index during the analyzed period. Save all results in a single table and show it in the _prompt_ of R.


Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: string
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "function 05"
exshuffle: TRUE

