```{r solution, echo = FALSE, eval=FALSE, results = "hide", message=FALSE}
say_my_name <- function(name_in) {
  # Print a single name in the prompt
  #
  # ARGS: name_in - Name to be printed
  #
  # RETURNS: TRUE, if sucessfull
  
  my_msg <- paste0('Your name is ', name_in)
  
  message(my_msg)
  
  # invisible will omit output if function is called without definition of output
  return(invisible(TRUE))
}

# testing
say_my_name('Marcelo')
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
my_answers <- rep(0, 5)
```

Question
========

Create a function called `say_my_name` that takes a person's name as input and shows the text _Your name is ..._ on the screen. Within the scope of the function, use comments to describe the purpose of the function, its inputs and outputs.


Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: string
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "function 01"
exshuffle: TRUE

