```{r solution, echo = FALSE, results = "hide", cache=TRUE}
my_link <- 'https://www.gutenberg.org/ebooks/2264.txt.utf-8'

my_book <- readr::read_lines(my_link)

# solution
my_sol <- length(my_book)
```

```{r datageneration, echo = FALSE, results = "hide"}
my_answers <- make_random_answers(my_sol)

#check_answers(my_answers)
```


Question
========

At the address [https://www.gutenberg.org/files/1342/1342-0.txt](https://www.gutenberg.org/files/1342/1342-0.txt) it is possible to access a file containing the full text of the book _Pride and Prejudice_ by Jane Austen. Use functions `download.file` and `readr::read_lines` to import the entire book as a vector of characters called `my_book` in R. How many lines does the resulting object have?

```{r questionlist, echo = FALSE, results = "asis"}
exams::answerlist(my_answers, markup = "markdown")
```

Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: num
exsolution: `r my_sol`
exname: "numeric "
exshuffle: TRUE

