```{r solution, echo = FALSE, results = "hide"}
total_shares <- 100
price_purchase <- 15

total_purchase_value <- total_shares*price_purchase

qtd_sell_1 <- 30
price_sell_1 <- 18
total_sell_1 <- qtd_sell_1*18

qtd_sell_2 <- total_shares-qtd_sell_1
price_sell_2 <- 22
total_sell_2 <- qtd_sell_2*price_sell_2

total_sell_value <- total_sell_1 + total_sell_2

# solution
my_sol <- total_sell_value - total_purchase_value
```

```{r datageneration, echo = FALSE, results = "hide"}
my_answers <- make_random_answers(my_sol, is_cash = TRUE)

#check_answers(my_answers)
```

Question
========

Let's assume that, on a certain date, you bought `r total_shares` shares in a company, paying `price_purchase` per share. After some time, you sold `r qtd_sell_1` shares for a `r price_sell_1` each and the remaining `r qtd_sell_2` shares were sold for `r price_sell_2` on a later day. Using a _script_ in R, structure this financial problem by creating numeric objects. What is the total gross profit from this sequence of transactions on the stock market?


```{r questionlist, echo = FALSE, results = "asis"}
exams::answerlist(my_answers, markup = "markdown")
```

Solution
================

```{r solution, eval=FALSE}
```

Meta-information
================
extype: schoice
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "numeric 01"
exshuffle: TRUE

