```{r solution, echo = FALSE, results = "hide", message=FALSE, eval=TRUE}
set.seed(5)

# number of obs
n_row <- 1000

# set x as Normal (0, 1)
x <- rnorm(n_row)

# set coefficients
my_alpha <- 1.5
my_beta <- 0.5

# build y
y <- my_alpha + my_beta*x + rnorm(n_row)

library(tidyverse)

my_lm <- lm(formula = y ~ x, data = tibble(x, y))

summary(my_lm)

library(gvlma)

# global validation of model
gvmodel <- gvlma(my_lm) 

# print result
summary(gvmodel)
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
#my_answers <- make_random_answers(my_sol)
my_answers <- rep(NA, 5)
```

Question
========

Use the `gvlma` package to test the OLS assumptions for the model previously estimated. Does the model pass all tests? If not, increase the value of `n_row` to 1000 and try again. Did the increase in the number of observations of the model impact the assumptions test? In what way?


Solution
================

The estimated model has not passed all the tests. In fact, not even the increase in the number of observations in the simulation resulted in the approval of the model in all aspects.

```{r solution, eval=FALSE}
```


Meta-information
================
extype: string
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "function 01"
exshuffle: TRUE

