```{r solution, echo = FALSE, results = "hide", message=FALSE, eval=TRUE}
set.seed(5)

# number of obs
n_row <- 100

# set x as Normal (0, 1)
x <- rnorm(n_row)

# set coefficients
my_alpha <- 1.5
my_beta <- 0.5

# build y
y <- my_alpha + my_beta*x + rnorm(n_row)

library(tidyverse)

my_lm <- lm(formula = y ~ x, data = tibble(x, y))

summary(my_lm)

my_sol <- coef(my_lm)[2]
```

```{r datageneration, echo = FALSE, results = "hide"}
# none
my_answers <- make_random_answers(my_sol)
```

Question
========

Simulate the following linear process in R:

```{r}
set.seed(5)

# number of obs
n_row <- 100

# set x as Normal (0, 1)
x <- rnorm(n_row)

# set coefficients
my_alpha <- 1.5
my_beta <- 0.5

# build y
y <- my_alpha + my_beta*x + rnorm(n_row)
```

Now, estimate a linear model where `x` is the explanatory variable and `y` is the explained variable. Use the `summary` function on the estimation return object to get more details about the model. What is the estimated beta value of the simulated data?

```{r questionlist, echo = FALSE, results = "asis"}
exams::answerlist(my_answers, markup = "markdown")
```

Solution
================

```{r solution, eval=FALSE}
```


Meta-information
================
extype: schoice
exsolution: `r mchoice2string(c(TRUE, FALSE, FALSE, FALSE, FALSE), single = TRUE)`
exname: "function 01"
exshuffle: TRUE

